\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
so long and thanks for all the fish

@@

>>>>

For the classification phase, we distributed the 94 articles evenly among the
three evaluators.
Each article has been read thoroughly and classified according to the
classification scheme if considered relevant to the study.

Misleading articles that passed screening phase were removed at that point.
A total of 39 articles have been rejected in this fashion.

@@

\subsection{Publication type distribution}
\begin{figure}
  \centering
  \includegraphics[scale=0.40]{doctype.png}
  \caption{Distribution of papers by type of document}
\end{figure}

% Need a graphic for article by publishers.
